---
title: "Data"
output: html_document
date: '2022-05-15'
---

Load every library needed
```{r, echo = FALSE, message = FALSE}
source(here::here("Setup/setup.R"))
```

In this first part, we download the data into R. Then, we will apply the necessary transformations on these data so that they can be correctly exploited for the following analysis.

The first thing we notice is the lack of observations for certain dates and time periods. Indeed, in order to perform our analyses, a database without missing values is essential. As our prediction of the number of bicycles used in the different stations of Gland must be done for every 10 minutes on May 25, 2022, our analysis must be done every 10 minutes for the time periods we have available (from .../.../... to .../.../...). 
We then eliminated a few days at the beginning of our database because it was information every 30 minutes. Also, we replaced the rest of the possible missing data by 0 or last value before that one ? , for a given station.  

--> describe more precisely what has been done for NAs

### Part 1 : Data preparation 


Load the dataset
```{r}
setwd(here::here("Data/")) # Where are the data sets needed
load("Bikesharing_dataset_final_2.RData")
Precipitation <- read.csv("order_103137_data.csv", sep = ";")
Temperature <- read.table("order_103200_data.txt", header = FALSE, sep = ";", colClasses = "character")
Ensoleillement <- read.table("order_103201_data.txt", header = FALSE, sep = ";", colClasses = "character")
Vent <- read.table("order_103202_data.txt", header = FALSE, sep = ";", colClasses = "character")
Pression <- read.table("order_103203_data.txt", header = FALSE, sep = ";", colClasses = "character")
```

Renaming the columns
```{r}
colnames(Precipitation) <- c("stn","Time","prec")
colnames(Temperature) <- c("stn","Time","temp")
colnames(Ensoleillement) <- c("stn","Time","ensoll")
colnames(Vent) <- c("stn","Time","vent")
colnames(Pression) <- c("stn","Time","press")
```

Building the Date column for weather data

```{r}
Precipitation <- Precipitation[c(-1,-2), ] #eliminate the first 2 row not needed
row.names(Precipitation) <- NULL #reset the index
```

```{r}
#first we need to set the temporal data as character data
Precipitation$Time <- as.character(Precipitation$Time) 
```

now for every weather variable we can select the numbers needed from their position into the character value and creating the year/month/day/hour/minute columns
```{r}

Precipitation$Year <- substr(Precipitation$Time,1,4)
Precipitation$Month <- substr(Precipitation$Time,5,6)
Precipitation$Day <- substr(Precipitation$Time,7,8)
Precipitation$Hour <- substr(Precipitation$Time,9,10)
Precipitation$Minute <- substr(Precipitation$Time,11,12)

Temperature$Year <- substr(Temperature$Time,1,4)
Temperature$Month <- substr(Temperature$Time,5,6)
Temperature$Day <- substr(Temperature$Time,7,8)
Temperature$Hour <- substr(Temperature$Time,9,10)
Temperature$Minute <- substr(Temperature$Time,11,12)

Ensoleillement$Year <- substr(Ensoleillement$Time,1,4)
Ensoleillement$Month <- substr(Ensoleillement$Time,5,6)
Ensoleillement$Day <- substr(Ensoleillement$Time,7,8)
Ensoleillement$Hour <- substr(Ensoleillement$Time,9,10)
Ensoleillement$Minute <- substr(Ensoleillement$Time,11,12)

Vent$Year <- substr(Vent$Time,1,4)
Vent$Month <- substr(Vent$Time,5,6)
Vent$Day <- substr(Vent$Time,7,8)
Vent$Hour <- substr(Vent$Time,9,10)
Vent$Minute <- substr(Vent$Time,11,12)

Pression$Year <- substr(Pression$Time,1,4)
Pression$Month <- substr(Pression$Time,5,6)
Pression$Day <- substr(Pression$Time,7,8)
Pression$Hour <- substr(Pression$Time,9,10)
Pression$Minute <- substr(Pression$Time,11,12)
```

Finally we can unite the values by selecting the same rows and adding the needed separators

```{r}
Precipitation$Date <- str_c(Precipitation$Year,"-",Precipitation$Month,"-",Precipitation$Day," ",Precipitation$Hour,":",Precipitation$Minute,":","00")
Temperature$Date <- str_c(Temperature$Year,"-",Temperature$Month,"-",Temperature$Day," ",Temperature$Hour,":",Temperature$Minute,":","00")
Ensoleillement$Date <- str_c(Ensoleillement$Year,"-",Ensoleillement$Month,"-",Ensoleillement$Day," ",Ensoleillement$Hour,":",Ensoleillement$Minute,":","00")
Vent$Date <- str_c(Vent$Year,"-",Vent$Month,"-",Vent$Day," ",Vent$Hour,":",Vent$Minute,":","00")
Pression$Date <- str_c(Pression$Year,"-",Pression$Month,"-",Pression$Day," ",Pression$Hour,":",Pression$Minute,":","00")
```



## Building the dataset for every Gland station

```{r}

Gland_Les_Tuillières <- series$`Gland, Les Tuillières` #select the station name from the series and converting into a data frame 
colnames(Gland_Les_Tuillières) <- c("Bike","E_Bike","Capacity","Date","Name","ID") #setting the column names

#repet for every station

Gland_Swissquote <- series$`Gland, Swissquote`
colnames(Gland_Swissquote) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Gare_Sud <- series$`Gland, Gare Sud, travaux, déplacée de 20m en mars-avril`
colnames(Gland_Gare_Sud) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_UICN <- series$`Gland, UICN`
colnames(Gland_UICN) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Montoly <- series$`Gland, Montoly`
colnames(Gland_Montoly) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Grand_Rue <- series$`Gland, Grand'Rue`
colnames(Gland_Grand_Rue) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_La_Falaise <- series$`Gland, La Falaise`
colnames(Gland_La_Falaise) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_La_Lignière <- series$`Gland, La Lignière`
colnames(Gland_La_Lignière) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Eikenott <- series$`Gland, Eikenott`
colnames(Gland_Eikenott) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_La_Dôle <- series$`Gland, La Dôle`
colnames(Gland_La_Dôle) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_En_Bord <- series$`Gland, En Bord`
colnames(Gland_En_Bord) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

```

The first 117 observations are 1 per our and not every 10 minuts, we eliminate them. 
```{r}
#discover the tot number of observation per station (every station has the same size, just one is needed) 
nobs <- nrow(Gland_Eikenott)

Gland_Eikenott <- Gland_Eikenott[c(118:nobs), ] #selecting only the observation with the right temporal mesure
row.names(Gland_Eikenott) <- NULL #reset the index
Gland_Eikenott$Name <- NULL #eliminate the column name
Gland_Eikenott$ID <- NULL #eliminate the column ID

#repet for every station

Gland_En_Bord_fin <- Gland_En_Bord[c(118:nobs), ]
row.names(Gland_En_Bord) <- NULL
Gland_En_Bord$Name <- NULL
Gland_En_Bord$ID <- NULL

Gland_Gare_Sud <- Gland_Gare_Sud[c(118:nobs), ]
row.names(Gland_Gare_Sud) <- NULL
Gland_Gare_Sud$Name <- NULL
Gland_Gare_Sud$ID <- NULL

Gland_Grand_Rue <- Gland_Grand_Rue[c(118:nobs), ]
row.names(Gland_Grand_Rue) <- NULL
Gland_Grand_Rue$Name <- NULL
Gland_Grand_Rue$ID <- NULL

Gland_La_Dôle <- Gland_La_Dôle[c(118:nobs), ]
row.names(Gland_La_Dôle) <- NULL
Gland_La_Dôle$Name <- NULL
Gland_La_Dôle$ID <- NULL

Gland_La_Falaise <- Gland_La_Falaise[c(118:nobs), ]
row.names(Gland_La_Falaise) <- NULL
Gland_La_Falaise$Name <- NULL
Gland_La_Falaise$ID <- NULL

Gland_Les_Tuillières <- Gland_Les_Tuillières[c(118:nobs), ]
row.names(Gland_Les_Tuillières) <- NULL
Gland_Les_Tuillières$Name <- NULL
Gland_Les_Tuillières$ID <- NULL

Gland_Montoly <- Gland_Montoly[c(118:nobs), ]
row.names(Gland_Montoly) <- NULL
Gland_Montoly$Name <- NULL
Gland_Montoly$ID <- NULL

Gland_Swissquote <- Gland_Swissquote[c(118:nobs), ]
row.names(Gland_Swissquote) <- NULL
Gland_Swissquote$Name <- NULL
Gland_Swissquote$ID <- NULL

Gland_UICN <- Gland_UICN[c(118:nobs), ]
row.names(Gland_UICN) <- NULL
Gland_UICN$Name <- NULL
Gland_UICN$ID <- NULL

Gland_La_Lignière <- Gland_La_Lignière[c(118:nobs), ]
row.names(Gland_La_Lignière) <- NULL
Gland_La_Lignière$Name <- NULL
Gland_La_Lignière$ID <- NULL

```

#searching for NA values
```{r}
which(is.na(Gland_Les_Tuillières))
which(is.na(Gland_Swissquote))
which(is.na(Gland_Gare_Sud))
which(is.na(Gland_UICN))
which(is.na(Gland_Montoly))
which(is.na(Gland_Grand_Rue))
which(is.na(Gland_La_Falaise))
which(is.na(Gland_La_Lignière))
which(is.na(Gland_Eikenott))
which(is.na(Gland_La_Dôle))
which(is.na(Gland_En_Bord))

```

no N/A found
First and last Date value for every dataset 

```{r}
Precipitation[ c(1,nrow(Precipitation)), "Date"]
Gland_Eikenott[ c(1,nrow(Gland_Eikenott)), "Date"]
Temperature[ c(1,nrow(Temperature)), "Date"] # same as pression, vent, and ensoleillement
```

Discover the first and the last observation that can be used to compare the different datasets by temporal data   
```{r}
Precipitation[Precipitation$Date=="2022-03-09 15:00:00", ]

Temperature[Temperature$Date=="2022-03-09 15:00:00", ]
Temperature[Temperature$Date=="2022-05-14 23:50:00", ]

Gland_Eikenott[Gland_Eikenott$Date=="2022-05-14 23:50:00", ] #BUG --> WHY? need to search the right observation by hand/eyes --> it is the number 9648
```

Eliminate the data not comparable
```{r}
Precipitation <- Precipitation[c(1243:nrow(Precipitation)), ] #select only the data needed
row.names(Precipitation) <- NULL #reset the index

#repet

Temperature <- Temperature[c(91:9648), ]
row.names(Temperature) <- NULL

Ensoleillement <- Ensoleillement[c(91:9648), ]
row.names(Ensoleillement) <- NULL

Vent <- Vent[c(91:9648), ]
row.names(Vent) <- NULL

Pression <- Pression[c(91:9648), ]
row.names(Pression) <- NULL

Gland_Eikenott <- Gland_Eikenott[c(1:9546), ]
Gland_En_Bord <- Gland_En_Bord[c(1:9546), ]
Gland_Gare_Sud <- Gland_Gare_Sud[c(1:9546), ]
Gland_Grand_Rue <- Gland_Grand_Rue[c(1:9546), ]
Gland_La_Dôle <- Gland_La_Dôle[c(1:9546), ]
Gland_La_Falaise <- Gland_La_Falaise[c(1:9546), ]
Gland_Les_Tuillières <- Gland_Les_Tuillières[c(1:9546), ]
Gland_Montoly <- Gland_Montoly[c(1:9546), ]
Gland_Swissquote <- Gland_Swissquote[c(1:9546), ]
Gland_UICN <- Gland_UICN[c(1:9546), ]
Gland_La_Lignière <- Gland_La_Lignière[c(1:9546), ]

#check the first and the last date
Gland_Eikenott[c(1,nrow(Gland_Eikenott)),"Date"]
Precipitation[c(1,nrow(Precipitation)),"Date"]
Temperature[c(1,nrow(Temperature)),"Date"]

#check the size of the datasets
nrow(Gland_Eikenott)
nrow(Precipitation)
nrow(Temperature)
```
The dates are correct, but the weather data have 12 observation more than the stations  --> it is needed to discover why

To compare the dates it is needed to solve the UTC difference --> conversion in both GMT

```{r}
#Weather variables

Precipitation$Date <- as.POSIXlt(Precipitation$Date, tz= " ") #converting the date value into POSIXlt and mantaining the space between date and hour
Precipitation$Date <- as.POSIXct(Precipitation$Date) #converting into POSIXct
Precipitation <- Precipitation[-c(1,2,4:8)] #eliminate useless columns 

#repeat

Temperature$Date <- as.POSIXlt(Temperature$Date, tz= " ")
Temperature$Date <- as.POSIXct(Temperature$Date)
Temperature <- Temperature[-c(1,2,4:8)]

Ensoleillement$Date <- as.POSIXlt(Ensoleillement$Date, tz= " ")
Ensoleillement$Date <- as.POSIXct(Ensoleillement$Date)
Ensoleillement <- Ensoleillement[-c(1,2,4:8)]

Vent$Date <- as.POSIXlt(Vent$Date, tz= " ")
Vent$Date <- as.POSIXct(Vent$Date)
Vent <- Vent[-c(1,2,4:8)]

Pression$Date <- as.POSIXlt(Pression$Date, tz= " ")
Pression$Date <- as.POSIXct(Pression$Date)
Pression <- Pression[-c(1,2,4:8)]

#Stations data

Gland_Eikenott$Date <- as.character(Gland_Eikenott$Date) #date as character
Gland_Eikenott$Date <- as.POSIXlt(Gland_Eikenott$Date, tz= " ") #repeat the weather procedure
Gland_Eikenott$Date <- as.POSIXct(Gland_Eikenott$Date)

#repeat

Gland_En_Bord$Date <- as.character(Gland_En_Bord$Date)
Gland_En_Bord$Date <- as.POSIXlt(Gland_En_Bord$Date, tz= " ")
Gland_En_Bord$Date <- as.POSIXct(Gland_En_Bord$Date)

Gland_Gare_Sud$Date <- as.character(Gland_Gare_Sud$Date)
Gland_Gare_Sud$Date <- as.POSIXlt(Gland_Gare_Sud$Date, tz= " ")
Gland_Gare_Sud$Date <- as.POSIXct(Gland_Gare_Sud$Date)

Gland_Grand_Rue$Date <- as.character(Gland_Grand_Rue$Date)
Gland_Grand_Rue$Date <- as.POSIXlt(Gland_Grand_Rue$Date, tz= " ")
Gland_Grand_Rue$Date <- as.POSIXct(Gland_Grand_Rue$Date)

Gland_La_Dôle$Date <- as.character(Gland_La_Dôle$Date)
Gland_La_Dôle$Date <- as.POSIXlt(Gland_La_Dôle$Date, tz= " ")
Gland_La_Dôle$Date <- as.POSIXct(Gland_La_Dôle$Date)

Gland_La_Falaise$Date <- as.character(Gland_La_Falaise$Date)
Gland_La_Falaise$Date <- as.POSIXlt(Gland_La_Falaise$Date, tz= " ")
Gland_La_Falaise$Date <- as.POSIXct(Gland_La_Falaise$Date)

Gland_Les_Tuillières$Date <- as.character(Gland_Les_Tuillières$Date)
Gland_Les_Tuillières$Date <- as.POSIXlt(Gland_Les_Tuillières$Date, tz= " ")
Gland_Les_Tuillières$Date <- as.POSIXct(Gland_Les_Tuillières$Date)

Gland_Montoly$Date <- as.character(Gland_Montoly$Date)
Gland_Montoly$Date <- as.POSIXlt(Gland_Montoly$Date, tz= " ")
Gland_Montoly$Date <- as.POSIXct(Gland_Montoly$Date)

Gland_Swissquote$Date <- as.character(Gland_Swissquote$Date)
Gland_Swissquote$Date <- as.POSIXlt(Gland_Swissquote$Date, tz= " ")
Gland_Swissquote$Date <- as.POSIXct(Gland_Swissquote$Date)

Gland_UICN$Date <- as.character(Gland_UICN$Date)
Gland_UICN$Date <- as.POSIXlt(Gland_UICN$Date, tz= " ")
Gland_UICN$Date <- as.POSIXct(Gland_UICN$Date)

Gland_La_Lignière$Date <- as.character(Gland_La_Lignière$Date)
Gland_La_Lignière$Date <- as.POSIXlt(Gland_La_Lignière$Date, tz= " ")
Gland_La_Lignière$Date <- as.POSIXct(Gland_La_Lignière$Date)

#final check
head(unique(Precipitation$Date))
head(unique(Temperature$Date))
head(unique(Gland_Eikenott$Date))
```

We compare
We select precipitation observations that have as date value a value not in common with station data
```{r}
Precipitation[!Precipitation$Date %in% Gland_Eikenott$Date, ]
```

Build a dataframe with dates not shared
```{r}
Date_to_add <- as.data.frame(c(Precipitation$Date[!Precipitation$Date %in% Gland_Eikenott$Date])) #create a data frame with just one column with the dates not shared 

Date_to_add <- Date_to_add%>%
  add_column(Bike = NA) %>% # add an empty column for Bike
  add_column(E_Bike = NA) %>% # add an empty column for E_Bike
  add_column(Capacity = NA) # add an empty column for Capacity

Date_to_add <- Date_to_add[ , c(2,3,4,1)] #same column position as station
names(Date_to_add)[4] <- "Date" #same column name

Date_to_add
```

Adding the missing dates to every station
```{r}
Gland_Eikenott <- bind_rows(Gland_Eikenott, Date_to_add) #add the missing rows
Gland_Eikenott <- Gland_Eikenott[order(Gland_Eikenott$Date), ] #order by date
row.names(Gland_Eikenott) <- NULL #reset the index

#repeat

Gland_En_Bord <- bind_rows(Gland_En_Bord, Date_to_add)
Gland_En_Bord <- Gland_En_Bord[order(Gland_En_Bord$Date), ]
row.names(Gland_En_Bord) <- NULL

Gland_Gare_Sud <- bind_rows(Gland_Gare_Sud, Date_to_add)
Gland_Gare_Sud <- Gland_Gare_Sud[order(Gland_Gare_Sud$Date), ]
row.names(Gland_Gare_Sud) <- NULL

Gland_Grand_Rue <- bind_rows(Gland_Grand_Rue, Date_to_add)
Gland_Grand_Rue <- Gland_Grand_Rue[order(Gland_Grand_Rue$Date), ]
row.names(Gland_Grand_Rue) <- NULL

Gland_La_Dôle <- bind_rows(Gland_La_Dôle, Date_to_add)
Gland_La_Dôle <- Gland_La_Dôle[order(Gland_La_Dôle$Date), ]
row.names(Gland_La_Dôle) <- NULL

Gland_La_Falaise <- bind_rows(Gland_La_Falaise, Date_to_add)
Gland_La_Falaise <- Gland_La_Falaise[order(Gland_La_Falaise$Date), ]
row.names(Gland_La_Falaise) <- NULL

Gland_Les_Tuillières <- bind_rows(Gland_Les_Tuillières, Date_to_add)
Gland_Les_Tuillières <- Gland_Les_Tuillières[order(Gland_Les_Tuillières$Date), ]
row.names(Gland_Les_Tuillières) <- NULL

Gland_Montoly <- bind_rows(Gland_Montoly, Date_to_add)
Gland_Montoly <- Gland_Montoly[order(Gland_Montoly$Date), ]
row.names(Gland_Montoly) <- NULL

Gland_Swissquote <- bind_rows(Gland_Swissquote, Date_to_add)
Gland_Swissquote <- Gland_Swissquote[order(Gland_Swissquote$Date), ]
row.names(Gland_Swissquote) <- NULL

Gland_UICN <- bind_rows(Gland_UICN, Date_to_add)
Gland_UICN <- Gland_UICN[order(Gland_UICN$Date), ]
row.names(Gland_UICN) <- NULL

Gland_La_Lignière <- bind_rows(Gland_La_Lignière, Date_to_add)
Gland_La_Lignière <- Gland_La_Lignière[order(Gland_La_Lignière$Date), ]
row.names(Gland_La_Lignière) <- NULL

```

# Final full dataset

```{r}
Gland_tot_clean <- bind_cols(Gland_Eikenott, Gland_En_Bord, Gland_Gare_Sud, Gland_Grand_Rue, Gland_La_Dôle, Gland_La_Falaise, Gland_La_Lignière, Gland_Les_Tuillières, Gland_Montoly, Gland_Swissquote, Gland_UICN, Precipitation, Temperature, Ensoleillement, Vent, Pression) #bind every data frame needed
Gland_fin <- Gland_tot_clean[-c(8,12,16,20,24,28,32,36,40,44,46,48,50,52,54)]
Gland_fin <- Gland_fin[ , c(4,1:3,5:39)]
```

Renaming the final dataset
```{r}
colnames(Gland_fin) <- c("Date","Bike_Eikenott", "Ebike_Eikenott", "Capacity_Eikenott", "Bike_En_Bord", "Ebike_En_Bord", "Capacity_En_Bord", "Bike_Gare_Sud", "Ebike_Gare_Sud", "Capacity_Gare_Sud", "Bike_Grand_Rue", "Ebike_Grand_Rue", "Capacity_Grand_Rue", "Bike_La_Dôle", "Ebike_La_Dôle", "Capacity_La_Dôle", "Bike_La_Falaise", "Ebike_La_Falaise", "Capacity_La_Falaise", "Bike_La_Lignière", "Ebike_La_Lignière", "Capacity_La_Lignière", "Bike_Les_Tuillières", "Ebike_Les_Tuillières", "Capacity_Les_Tuillières", "Bike_Montoly", "Ebike_Montoly", "Capacity_Montoly", "Bike_Swissquote", "Ebike_Swissquote", "Capacity_Swissquote", "Bike_UICN", "Ebike_UICN", "Capacity_UICN","prec","temp","ensoll","vent","press")

Gland_fin$prec <- as.numeric(Gland_fin$prec)
Gland_fin$temp <- as.numeric(Gland_fin$temp)
Gland_fin$ensoll <- as.numeric(Gland_fin$ensoll)
Gland_fin$vent <- as.numeric(Gland_fin$vent)
Gland_fin$press <- as.numeric(Gland_fin$press)

head(Gland_fin)
```


The first dataset is now ready to be used. 


#### PART 2 -> NEW DATA

Building the dataset for every Gland station

```{r}

Gland_Les_Tuillières_fin <- series$`Gland, Les Tuillières` #select the station name from the series and converting into a data frame 
colnames(Gland_Les_Tuillières_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID") #setting the column names

#repet for every station

Gland_Swissquote_fin <- series$`Gland, Swissquote`
colnames(Gland_Swissquote_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Gare_Sud_fin <- series$`Gland, Gare Sud, travaux, déplacée de 20m en mars-avril`
colnames(Gland_Gare_Sud_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_UICN_fin <- series$`Gland, UICN`
colnames(Gland_UICN_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Montoly_fin <- series$`Gland, Montoly`
colnames(Gland_Montoly_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Grand_Rue_fin <- series$`Gland, Grand'Rue`
colnames(Gland_Grand_Rue_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_La_Falaise_fin <- series$`Gland, La Falaise`
colnames(Gland_La_Falaise_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_La_Lignière_fin <- series$`Gland, La Lignière`
colnames(Gland_La_Lignière_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_Eikenott_fin <- series$`Gland, Eikenott`
colnames(Gland_Eikenott_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_La_Dôle_fin <- series$`Gland, La Dôle`
colnames(Gland_La_Dôle_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

Gland_En_Bord_fin <- series$`Gland, En Bord`
colnames(Gland_En_Bord_fin) <- c("Bike","E_Bike","Capacity","Date","Name","ID")

```

#The first 117 observations are 1 per our and not every 10 minuts -> eliminate
```{r}
#discover the tot number of observation per station (every station has the same size, just one is needed) 
nobs2 <- nrow(Gland_Eikenott_fin)

Gland_Eikenott_fin <- Gland_Eikenott_fin[c(118:nobs2), ] #selecting only the observation with the right temporal mesure
row.names(Gland_Eikenott_fin) <- NULL #reset the index
Gland_Eikenott_fin$Name <- NULL #eliminate the column name
Gland_Eikenott_fin$ID <- NULL #eliminate the column ID

#repet for every station

Gland_En_Bord_fin <- Gland_En_Bord_fin[c(118:nobs2), ]
row.names(Gland_En_Bord_fin) <- NULL
Gland_En_Bord_fin$Name <- NULL
Gland_En_Bord_fin$ID <- NULL

Gland_Gare_Sud_fin <- Gland_Gare_Sud_fin[c(118:nobs2), ]
row.names(Gland_Gare_Sud_fin) <- NULL
Gland_Gare_Sud_fin$Name <- NULL
Gland_Gare_Sud_fin$ID <- NULL

Gland_Grand_Rue_fin <- Gland_Grand_Rue_fin[c(118:nobs2), ]
row.names(Gland_Grand_Rue_fin) <- NULL
Gland_Grand_Rue_fin$Name <- NULL
Gland_Grand_Rue_fin$ID <- NULL

Gland_La_Dôle_fin <- Gland_La_Dôle_fin[c(118:nobs2), ]
row.names(Gland_La_Dôle_fin) <- NULL
Gland_La_Dôle_fin$Name <- NULL
Gland_La_Dôle_fin$ID <- NULL

Gland_La_Falaise_fin <- Gland_La_Falaise_fin[c(118:nobs2), ]
row.names(Gland_La_Falaise_fin) <- NULL
Gland_La_Falaise_fin$Name <- NULL
Gland_La_Falaise_fin$ID <- NULL

Gland_Les_Tuillières_fin <- Gland_Les_Tuillières_fin[c(118:nobs2), ]
row.names(Gland_Les_Tuillières_fin) <- NULL
Gland_Les_Tuillières_fin$Name <- NULL
Gland_Les_Tuillières_fin$ID <- NULL

Gland_Montoly_fin <- Gland_Montoly_fin[c(118:nobs2), ]
row.names(Gland_Montoly_fin) <- NULL
Gland_Montoly_fin$Name <- NULL
Gland_Montoly_fin$ID <- NULL

Gland_Swissquote_fin <- Gland_Swissquote_fin[c(118:nobs2), ]
row.names(Gland_Swissquote_fin) <- NULL
Gland_Swissquote_fin$Name <- NULL
Gland_Swissquote_fin$ID <- NULL

Gland_UICN_fin <- Gland_UICN_fin[c(118:nobs2), ]
row.names(Gland_UICN_fin) <- NULL
Gland_UICN_fin$Name <- NULL
Gland_UICN_fin$ID <- NULL

Gland_La_Lignière_fin <- Gland_La_Lignière_fin[c(118:nobs2), ]
row.names(Gland_La_Lignière_fin) <- NULL
Gland_La_Lignière_fin$Name <- NULL
Gland_La_Lignière_fin$ID <- NULL

```

```{r}
Gland_tot_clean_fin <- bind_cols(Gland_Eikenott_fin, Gland_En_Bord_fin, Gland_Gare_Sud_fin, Gland_Grand_Rue_fin, Gland_La_Dôle_fin, Gland_La_Falaise_fin, Gland_La_Lignière_fin, Gland_Les_Tuillières_fin, Gland_Montoly_fin, Gland_Swissquote_fin, Gland_UICN_fin) #bind every data frame needed
Gland_fin_2 <- Gland_tot_clean_fin[-c(8,12,16,20,24,28,32,36,40,44)]
Gland_fin_2 <- Gland_fin_2[ , c(4,1:3,5:34)]
```

```{r}
colnames(Gland_fin_2) <- c("Date","Bike_Eikenott", "Ebike_Eikenott", "Capacity_Eikenott", "Bike_En_Bord", "Ebike_En_Bord", "Capacity_En_Bord", "Bike_Gare_Sud", "Ebike_Gare_Sud", "Capacity_Gare_Sud", "Bike_Grand_Rue", "Ebike_Grand_Rue", "Capacity_Grand_Rue", "Bike_La_Dôle", "Ebike_La_Dôle", "Capacity_La_Dôle", "Bike_La_Falaise", "Ebike_La_Falaise", "Capacity_La_Falaise", "Bike_La_Lignière", "Ebike_La_Lignière", "Capacity_La_Lignière", "Bike_Les_Tuillières", "Ebike_Les_Tuillières", "Capacity_Les_Tuillières", "Bike_Montoly", "Ebike_Montoly", "Capacity_Montoly", "Bike_Swissquote", "Ebike_Swissquote", "Capacity_Swissquote", "Bike_UICN", "Ebike_UICN", "Capacity_UICN")
```

```{r}

Gland_fin_2 <- Gland_fin_2 %>% pad()

```


The second bike dataset of the most updated data is ready to be used. 
