---
title: "Data"
output: html_document
date: '2022-05-15'
---

```{r, echo = FALSE, message = FALSE}
source(here::here("Setup/setup.R"))
```

### Part 1 : Data preparation 

Load the dataset
```{r}
setwd(here::here("Data/")) # Where are the data sets
load("Bikesharing_dataset_fin.RData")
Precipitation <- read.csv("order_103137_data.csv", sep = ";")
Temperature <- read.table("order_103200_data.txt", header = FALSE, sep = ";", colClasses = "character")
Ensoleillement <- read.table("order_103201_data.txt", header = FALSE, sep = ";", colClasses = "character")
Vent <- read.table("order_103202_data.txt", header = FALSE, sep = ";", colClasses = "character")
Pression <- read.table("order_103203_data.txt", header = FALSE, sep = ";", colClasses = "character")
```
Renaming the columns
```{r}
colnames(Precipitation) <- c("stn","Time","prec")
colnames(Temperature) <- c("stn","Time","temp")
colnames(Ensoleillement) <- c("stn","Time","ensoll")
colnames(Vent) <- c("stn","Time","vent")
colnames(Pression) <- c("stn","Time","press")
```

Building the Date column for weather data
```{r}
Precipitation <- Precipitation[c(-1,-2), ] #eliminate the first 2 row not needed
row.names(Precipitation) <- NULL #reset the index
```
First we need to set the temporal data as character data
```{r}
Precipitation$Time <- as.character(Precipitation$Time) 
```

Now for every weather variable we can select the numbers needed from their position into the character value and creating the year/month/day/hour/minute columns.
```{r}
Precipitation$Year <- substr(Precipitation$Time,1,4)
Precipitation$Month <- substr(Precipitation$Time,5,6)
Precipitation$Day <- substr(Precipitation$Time,7,8)
Precipitation$Hour <- substr(Precipitation$Time,9,10)
Precipitation$Minute <- substr(Precipitation$Time,11,12)

Temperature$Year <- substr(Temperature$Time,1,4)
Temperature$Month <- substr(Temperature$Time,5,6)
Temperature$Day <- substr(Temperature$Time,7,8)
Temperature$Hour <- substr(Temperature$Time,9,10)
Temperature$Minute <- substr(Temperature$Time,11,12)

Ensoleillement$Year <- substr(Ensoleillement$Time,1,4)
Ensoleillement$Month <- substr(Ensoleillement$Time,5,6)
Ensoleillement$Day <- substr(Ensoleillement$Time,7,8)
Ensoleillement$Hour <- substr(Ensoleillement$Time,9,10)
Ensoleillement$Minute <- substr(Ensoleillement$Time,11,12)

Vent$Year <- substr(Vent$Time,1,4)
Vent$Month <- substr(Vent$Time,5,6)
Vent$Day <- substr(Vent$Time,7,8)
Vent$Hour <- substr(Vent$Time,9,10)
Vent$Minute <- substr(Vent$Time,11,12)

Pression$Year <- substr(Pression$Time,1,4)
Pression$Month <- substr(Pression$Time,5,6)
Pression$Day <- substr(Pression$Time,7,8)
Pression$Hour <- substr(Pression$Time,9,10)
Pression$Minute <- substr(Pression$Time,11,12)
```

Finally we can unite the values by selecting the same rows and adding the needed separators
```{r}
Precipitation$Date <- str_c(Precipitation$Year,"-",Precipitation$Month,"-",Precipitation$Day," ",Precipitation$Hour,":",Precipitation$Minute,":","00")
Temperature$Date <- str_c(Temperature$Year,"-",Temperature$Month,"-",Temperature$Day," ",Temperature$Hour,":",Temperature$Minute,":","00")
Ensoleillement$Date <- str_c(Ensoleillement$Year,"-",Ensoleillement$Month,"-",Ensoleillement$Day," ",Ensoleillement$Hour,":",Ensoleillement$Minute,":","00")
Vent$Date <- str_c(Vent$Year,"-",Vent$Month,"-",Vent$Day," ",Vent$Hour,":",Vent$Minute,":","00")
Pression$Date <- str_c(Pression$Year,"-",Pression$Month,"-",Pression$Day," ",Pression$Hour,":",Pression$Minute,":","00")
```

Building the dataset for every Gland station
```{r}
Gland_Les_Tuillières <- as.data.frame(series["Gland, Les Tuillières"]) #select the station name from the series and converting into a data frame 
colnames(Gland_Les_Tuillières) <- c("Bike","E_Bike","Capacity","Date","Name") #setting the column names

#repet for every station

Gland_Swissquote <- as.data.frame(series["Gland, Swissquote"])
colnames(Gland_Swissquote) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Gare_Sud <- as.data.frame(series["Gland, Gare Sud, travaux, déplacée de 20m en mars-avril"])
colnames(Gland_Gare_Sud) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_UICN <- as.data.frame(series["Gland, UICN"])
colnames(Gland_UICN) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Montoly <- as.data.frame(series["Gland, Montoly"])
colnames(Gland_Montoly) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Grand_Rue <- as.data.frame(series["Gland, Grand'Rue"])
colnames(Gland_Grand_Rue) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_La_Falaise <- as.data.frame(series["Gland, La Falaise"])
colnames(Gland_La_Falaise) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_La_Lignière <- as.data.frame(series["Gland, La Lignière"])
colnames(Gland_La_Lignière) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Eikenott <- as.data.frame(series["Gland, Eikenott"])
colnames(Gland_Eikenott) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_La_Dôle <- as.data.frame(series["Gland, La Dôle"])
colnames(Gland_La_Dôle) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_En_Bord <- as.data.frame(series["Gland, En Bord"])
colnames(Gland_En_Bord) <- c("Bike","E_Bike","Capacity","Date","Name")
```

Searching for NA values
```{r}
which(is.na(Gland_Les_Tuillières))
which(is.na(Gland_Swissquote))
which(is.na(Gland_Gare_Sud))
which(is.na(Gland_UICN))
which(is.na(Gland_Montoly))
which(is.na(Gland_Grand_Rue))
which(is.na(Gland_La_Falaise))
which(is.na(Gland_La_Lignière))
which(is.na(Gland_Eikenott))
which(is.na(Gland_La_Dôle))
which(is.na(Gland_En_Bord))
```
no N/A found

The first 117 observations are 1 per our and not every 10 minuts -> eliminate
```{r}
#discover the tot number of observation per station (every station has the same size, just one is needed) 
nobs <- nrow(Gland_Eikenott)

Gland_Eikenott <- Gland_Eikenott[c(118:nobs), ] #selecting only the observation with the right temporal mesure
row.names(Gland_Eikenott) <- NULL #reset the index
Gland_Eikenott$Name <- NULL #eliminate the column name

#repet for every station

Gland_En_Bord <- Gland_En_Bord[c(118:nobs), ]
row.names(Gland_En_Bord) <- NULL
Gland_En_Bord$Name <- NULL

Gland_Gare_Sud <- Gland_Gare_Sud[c(118:nobs), ]
row.names(Gland_Gare_Sud) <- NULL
Gland_Gare_Sud$Name <- NULL

Gland_Grand_Rue <- Gland_Grand_Rue[c(118:nobs), ]
row.names(Gland_Grand_Rue) <- NULL
Gland_Grand_Rue$Name <- NULL

Gland_La_Dôle <- Gland_La_Dôle[c(118:nobs), ]
row.names(Gland_La_Dôle) <- NULL
Gland_La_Dôle$Name <- NULL

Gland_La_Falaise <- Gland_La_Falaise[c(118:nobs), ]
row.names(Gland_La_Falaise) <- NULL
Gland_La_Falaise$Name <- NULL

Gland_Les_Tuillières <- Gland_Les_Tuillières[c(118:nobs), ]
row.names(Gland_Les_Tuillières) <- NULL
Gland_Les_Tuillières$Name <- NULL

Gland_Montoly <- Gland_Montoly[c(118:nobs), ]
row.names(Gland_Montoly) <- NULL
Gland_Montoly$Name <- NULL

Gland_Swissquote <- Gland_Swissquote[c(118:nobs), ]
row.names(Gland_Swissquote) <- NULL
Gland_Swissquote$Name <- NULL

Gland_UICN <- Gland_UICN[c(118:nobs), ]
row.names(Gland_UICN) <- NULL
Gland_UICN$Name <- NULL

Gland_La_Lignière <- Gland_La_Lignière[c(118:nobs), ]
row.names(Gland_La_Lignière) <- NULL
Gland_La_Lignière$Name <- NULL

```

First and last Date value for every dataset 
```{r}
Precipitation[ c(1,nrow(Precipitation)), "Date"]
Gland_Eikenott[ c(1,nrow(Gland_Eikenott)), "Date"]
Temperature[ c(1,nrow(Temperature)), "Date"] # same as pression, vent, and ensoleillement
```

Discover the first and the last observation that can be used to compare the different datasets by temporal data   
```{r}
Precipitation[Precipitation$Date=="2022-03-09 15:00:00", ]

Temperature[Temperature$Date=="2022-03-09 15:00:00", ]
Temperature[Temperature$Date=="2022-05-14 23:50:00", ]

Gland_Eikenott[Gland_Eikenott$Date=="2022-05-14 23:50:00", ] #BUG --> WHY? need to search the right observation by hand/eyes --> it is the number 9648
```

Eliminate the data not comparable
```{r}
Precipitation <- Precipitation[c(1243:nrow(Precipitation)), ] #select only the data needed
row.names(Precipitation) <- NULL #reset the index

#repet

Temperature <- Temperature[c(91:9648), ]
row.names(Temperature) <- NULL

Ensoleillement <- Ensoleillement[c(91:9648), ]
row.names(Ensoleillement) <- NULL

Vent <- Vent[c(91:9648), ]
row.names(Vent) <- NULL

Pression <- Pression[c(91:9648), ]
row.names(Pression) <- NULL

Gland_Eikenott <- Gland_Eikenott[c(1:9546), ]
Gland_En_Bord <- Gland_En_Bord[c(1:9546), ]
Gland_Gare_Sud <- Gland_Gare_Sud[c(1:9546), ]
Gland_Grand_Rue <- Gland_Grand_Rue[c(1:9546), ]
Gland_La_Dôle <- Gland_La_Dôle[c(1:9546), ]
Gland_La_Falaise <- Gland_La_Falaise[c(1:9546), ]
Gland_Les_Tuillières <- Gland_Les_Tuillières[c(1:9546), ]
Gland_Montoly <- Gland_Montoly[c(1:9546), ]
Gland_Swissquote <- Gland_Swissquote[c(1:9546), ]
Gland_UICN <- Gland_UICN[c(1:9546), ]
Gland_La_Lignière <- Gland_La_Lignière[c(1:9546), ]

#check the first and the last date
Gland_Eikenott[c(1,nrow(Gland_Eikenott)),"Date"]
Precipitation[c(1,nrow(Precipitation)),"Date"]
Temperature[c(1,nrow(Temperature)),"Date"]

#check the size of the datasets
nrow(Gland_Eikenott)
nrow(Precipitation)
nrow(Temperature)
```
The dates are correct, but the weather data have 12 observation more than the stations  --> it is needed to discover why

To compare the dates it is needed to solve the UTC difference --> conversion in both GMT
```{r}
#Weather variables

Precipitation$Date <- as.POSIXlt(Precipitation$Date, tz= " ") #converting the date value into POSIXlt and mantaining the space between date and hour
Precipitation$Date <- as.POSIXct(Precipitation$Date) #converting into POSIXct
Precipitation <- Precipitation[-c(1,2,4:8)] #eliminate useless columns 

#repeat

Temperature$Date <- as.POSIXlt(Temperature$Date, tz= " ")
Temperature$Date <- as.POSIXct(Temperature$Date)
Temperature <- Temperature[-c(1,2,4:8)]

Ensoleillement$Date <- as.POSIXlt(Ensoleillement$Date, tz= " ")
Ensoleillement$Date <- as.POSIXct(Ensoleillement$Date)
Ensoleillement <- Ensoleillement[-c(1,2,4:8)]

Vent$Date <- as.POSIXlt(Vent$Date, tz= " ")
Vent$Date <- as.POSIXct(Vent$Date)
Vent <- Vent[-c(1,2,4:8)]

Pression$Date <- as.POSIXlt(Pression$Date, tz= " ")
Pression$Date <- as.POSIXct(Pression$Date)
Pression <- Pression[-c(1,2,4:8)]

#Stations data

Gland_Eikenott$Date <- as.character(Gland_Eikenott$Date) #date as character
Gland_Eikenott$Date <- as.POSIXlt(Gland_Eikenott$Date, tz= " ") #repeat the weather procedure
Gland_Eikenott$Date <- as.POSIXct(Gland_Eikenott$Date)

#repeat

Gland_En_Bord$Date <- as.character(Gland_En_Bord$Date)
Gland_En_Bord$Date <- as.POSIXlt(Gland_En_Bord$Date, tz= " ")
Gland_En_Bord$Date <- as.POSIXct(Gland_En_Bord$Date)

Gland_Gare_Sud$Date <- as.character(Gland_Gare_Sud$Date)
Gland_Gare_Sud$Date <- as.POSIXlt(Gland_Gare_Sud$Date, tz= " ")
Gland_Gare_Sud$Date <- as.POSIXct(Gland_Gare_Sud$Date)

Gland_Grand_Rue$Date <- as.character(Gland_Grand_Rue$Date)
Gland_Grand_Rue$Date <- as.POSIXlt(Gland_Grand_Rue$Date, tz= " ")
Gland_Grand_Rue$Date <- as.POSIXct(Gland_Grand_Rue$Date)

Gland_La_Dôle$Date <- as.character(Gland_La_Dôle$Date)
Gland_La_Dôle$Date <- as.POSIXlt(Gland_La_Dôle$Date, tz= " ")
Gland_La_Dôle$Date <- as.POSIXct(Gland_La_Dôle$Date)

Gland_La_Falaise$Date <- as.character(Gland_La_Falaise$Date)
Gland_La_Falaise$Date <- as.POSIXlt(Gland_La_Falaise$Date, tz= " ")
Gland_La_Falaise$Date <- as.POSIXct(Gland_La_Falaise$Date)

Gland_Les_Tuillières$Date <- as.character(Gland_Les_Tuillières$Date)
Gland_Les_Tuillières$Date <- as.POSIXlt(Gland_Les_Tuillières$Date, tz= " ")
Gland_Les_Tuillières$Date <- as.POSIXct(Gland_Les_Tuillières$Date)

Gland_Montoly$Date <- as.character(Gland_Montoly$Date)
Gland_Montoly$Date <- as.POSIXlt(Gland_Montoly$Date, tz= " ")
Gland_Montoly$Date <- as.POSIXct(Gland_Montoly$Date)

Gland_Swissquote$Date <- as.character(Gland_Swissquote$Date)
Gland_Swissquote$Date <- as.POSIXlt(Gland_Swissquote$Date, tz= " ")
Gland_Swissquote$Date <- as.POSIXct(Gland_Swissquote$Date)

Gland_UICN$Date <- as.character(Gland_UICN$Date)
Gland_UICN$Date <- as.POSIXlt(Gland_UICN$Date, tz= " ")
Gland_UICN$Date <- as.POSIXct(Gland_UICN$Date)

Gland_La_Lignière$Date <- as.character(Gland_La_Lignière$Date)
Gland_La_Lignière$Date <- as.POSIXlt(Gland_La_Lignière$Date, tz= " ")
Gland_La_Lignière$Date <- as.POSIXct(Gland_La_Lignière$Date)

#final check
head(unique(Precipitation$Date))
head(unique(Temperature$Date))
head(unique(Gland_Eikenott$Date))
```

Compare, we select precipitation observations that have as date value a value not in common with station data
```{r}
Precipitation[!Precipitation$Date %in% Gland_Eikenott$Date, ]
```

Build a dataframe with dates not shared
```{r}
Date_to_add <- as.data.frame(c(Precipitation$Date[!Precipitation$Date %in% Gland_Eikenott$Date])) #create a data frame with just one column with the dates not shared 

Date_to_add <- Date_to_add%>%
  add_column(Bike = NA) %>% # add an empty column for Bike
  add_column(E_Bike = NA) %>% # add an empty column for E_Bike
  add_column(Capacity = NA) # add an empty column for Capacity

Date_to_add <- Date_to_add[ , c(2,3,4,1)] #same column position as station
names(Date_to_add)[4] <- "Date" #same column name

Date_to_add
```

Adding the missing dates to every station
```{r}
Gland_Eikenott <- bind_rows(Gland_Eikenott, Date_to_add) #add the missing rows
Gland_Eikenott <- Gland_Eikenott[order(Gland_Eikenott$Date), ] #order by date
row.names(Gland_Eikenott) <- NULL #reset the index

#repeat

Gland_En_Bord <- bind_rows(Gland_En_Bord, Date_to_add)
Gland_En_Bord <- Gland_En_Bord[order(Gland_En_Bord$Date), ]
row.names(Gland_En_Bord) <- NULL

Gland_Gare_Sud <- bind_rows(Gland_Gare_Sud, Date_to_add)
Gland_Gare_Sud <- Gland_Gare_Sud[order(Gland_Gare_Sud$Date), ]
row.names(Gland_Gare_Sud) <- NULL

Gland_Grand_Rue <- bind_rows(Gland_Grand_Rue, Date_to_add)
Gland_Grand_Rue <- Gland_Grand_Rue[order(Gland_Grand_Rue$Date), ]
row.names(Gland_Grand_Rue) <- NULL

Gland_La_Dôle <- bind_rows(Gland_La_Dôle, Date_to_add)
Gland_La_Dôle <- Gland_La_Dôle[order(Gland_La_Dôle$Date), ]
row.names(Gland_La_Dôle) <- NULL

Gland_La_Falaise <- bind_rows(Gland_La_Falaise, Date_to_add)
Gland_La_Falaise <- Gland_La_Falaise[order(Gland_La_Falaise$Date), ]
row.names(Gland_La_Falaise) <- NULL

Gland_Les_Tuillières <- bind_rows(Gland_Les_Tuillières, Date_to_add)
Gland_Les_Tuillières <- Gland_Les_Tuillières[order(Gland_Les_Tuillières$Date), ]
row.names(Gland_Les_Tuillières) <- NULL

Gland_Montoly <- bind_rows(Gland_Montoly, Date_to_add)
Gland_Montoly <- Gland_Montoly[order(Gland_Montoly$Date), ]
row.names(Gland_Montoly) <- NULL

Gland_Swissquote <- bind_rows(Gland_Swissquote, Date_to_add)
Gland_Swissquote <- Gland_Swissquote[order(Gland_Swissquote$Date), ]
row.names(Gland_Swissquote) <- NULL

Gland_UICN <- bind_rows(Gland_UICN, Date_to_add)
Gland_UICN <- Gland_UICN[order(Gland_UICN$Date), ]
row.names(Gland_UICN) <- NULL

Gland_La_Lignière <- bind_rows(Gland_La_Lignière, Date_to_add)
Gland_La_Lignière <- Gland_La_Lignière[order(Gland_La_Lignière$Date), ]
row.names(Gland_La_Lignière) <- NULL

```

Final full dataset

```{r}
Gland_tot_clean <- bind_cols(Gland_Eikenott, Gland_En_Bord, Gland_Gare_Sud, Gland_Grand_Rue, Gland_La_Dôle, Gland_La_Falaise, Gland_La_Lignière, Gland_Les_Tuillières, Gland_Montoly, Gland_Swissquote, Gland_UICN, Precipitation, Temperature, Ensoleillement, Vent, Pression) #bind every data frame needed
Gland_fin <- Gland_tot_clean[-c(8,12,16,20,24,28,32,36,40,44,46,48,50,52,54)]
Gland_fin <- Gland_fin[ , c(4,1:3,5:39)]
```

Renaming the final dataset
```{r}
colnames(Gland_fin) <- c("Date","Bike_Eikenott", "Ebike_Eikenott", "Capacity_Eikenott", "Bike_En_Bord", "Ebike_En_Bord", "Capacity_En_Bord", "Bike_Gare_Sud", "Ebike_Gare_Sud", "Capacity_Gare_Sud", "Bike_Grand_Rue", "Ebike_Grand_Rue", "Capacity_Grand_Rue", "Bike_La_Dôle", "Ebike_La_Dôle", "Capacity_La_Dôle", "Bike_La_Falaise", "Ebike_La_Falaise", "Capacity_La_Falaise", "Bike_La_Lignière", "Ebike_La_Lignière", "Capacity_La_Lignière", "Bike_Les_Tuillières", "Ebike_Les_Tuillières", "Capacity_Les_Tuillières", "Bike_Montoly", "Ebike_Montoly", "Capacity_Montoly", "Bike_Swissquote", "Ebike_Swissquote", "Capacity_Swissquote", "Bike_UICN", "Ebike_UICN", "Capacity_UICN","prec","temp","ensoll","vent","press")

Gland_fin$prec <- as.numeric(Gland_fin$prec)
Gland_fin$temp <- as.numeric(Gland_fin$temp)
Gland_fin$ensoll <- as.numeric(Gland_fin$ensoll)
Gland_fin$vent <- as.numeric(Gland_fin$vent)
Gland_fin$press <- as.numeric(Gland_fin$press)

head(Gland_fin)
```

The dataset is now ready to be used. 



The city of Gland has 11 stations and each of them has either classic bikes or electric bikes (e-bike). This includes 1858 observations and 2 variables for each station and each type of bike.
**Stations**:
1. Gland_Les_Tuillières 
2. Gland_Swissquote 
3. Gland_Gare_Sud
4. Gland_UICN 
5. Gland_Montoly 
6. Gland_Grande_Rue 
7. Gland_La_Falaise 
8. Gland_La_Lignère 
9. Gland_Eikenott 
10. Gland_La_Dôle 
11. Gland_En_Bord 
**Variables**
1. Date : *date* Borrowing date of the bike
2. Bike : *num* Number of the borrowed bike 
