---
title: "Eda"
output: html_document
date: '2022-05-15'
---

#Load every library needed
```{r, echo = FALSE, message = FALSE}
source(here::here("Setup/setup.R"))
```

### Part 2 : Exploratory Data Analysis (EDA)


To plot different variable in the same graph they need to be comparble
```{r}
#search for a max Bike and EBike value for every station
max(Gland_fin[ , c(2,3,5,6,8,9,11,12,14,15,17,18,20,21,23,24,26,27,29,30,32,33)], na.rm = TRUE)
#The max number of bycicle in a station is 12, so we will scale the weather variables from 0 to 12
```
Scaling process
```{r}
#internal variance
diff_prec <- max(Gland_fin$prec, na.rm = TRUE) - min(Gland_fin$prec, na.rm = TRUE)
diff_temp <- max(Gland_fin$temp, na.rm = TRUE) - min(Gland_fin$temp, na.rm = TRUE)
diff_ensoll <- max(Gland_fin$ensoll, na.rm = TRUE) - min(Gland_fin$ensoll, na.rm = TRUE)
diff_vent <- max(Gland_fin$vent, na.rm = TRUE) - min(Gland_fin$vent, na.rm = TRUE)
diff_press <- max(Gland_fin$press, na.rm = TRUE) - min(Gland_fin$press, na.rm = TRUE)
#minimum
min_prec <- min(Gland_fin$prec, na.rm = TRUE)
min_temp <- min(Gland_fin$temp, na.rm = TRUE)
min_ensoll <- min(Gland_fin$ensoll, na.rm = TRUE)
min_vent <- min(Gland_fin$vent, na.rm = TRUE)
min_press <- min(Gland_fin$press, na.rm = TRUE)
#final formula to obtain datas from 0 to 12
Gland_fin$prec_comp <- (Gland_fin$prec - min_prec)*12/diff_prec
Gland_fin$temp_comp <- (Gland_fin$temp - min_temp)*12/diff_temp
Gland_fin$ensoll_comp <- (Gland_fin$ensoll - min_ensoll)*12/diff_ensoll
Gland_fin$vent_comp <- (Gland_fin$vent - min_vent)*12/diff_vent
Gland_fin$press_comp <- (Gland_fin$press - min_press)*12/diff_press
```

We first look at the data. We are interested in forecasting the numbers of bike and ebike needed in the different stations, so here we plot the number of this 2 variables and the stations capacities sorted by time.
```{r}

#plot weather data
#ensoleillement has to be eliminate from the graphs --> every day from min to max --> impossible to see
colors <- c("Precipitation" = "blue", "Temperature" = "red", "Vent" = "Green", "Pression" = "orange")

ggplot(Gland_fin ,aes(x=Date))+
  geom_line(aes(y=temp_comp, color="Temperature"))+
  geom_line(aes(y=vent_comp, color="Vent"))+
  geom_line(aes(y=press_comp, color="Pression"))+
  geom_line(aes(y=prec_comp, color="Precipitation"))+
  labs(x="Time", y="Intensity", color="Legend")+
  scale_color_manual(values = colors)

ggplot(Gland_fin ,aes(x=Date))+
  geom_point(aes(y=temp_comp, color="Temperature"))+
  geom_point(aes(y=vent_comp, color="Vent"))+
  geom_point(aes(y=press_comp, color="Pression"))+
  geom_point(aes(y=prec_comp, color="Precipitation"))+
  labs(x="Time", y="Intensity", color="Legend")+
  scale_color_manual(values = colors)

#plot some station data
ggplot()+
  geom_line(data = Gland_Swissquote, aes(y=Bike, x=Date, color = "red")) +
  geom_line(data = Gland_Swissquote, aes(y=E_Bike, x=Date, Color = "blue")) +
  ggtitle("Gland_Swissquote")

ggplot()+
  geom_line(data = Gland_Gare_Sud, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Gare_Sud, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Gare_Sud, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Gare_Sud")

ggplot()+
  geom_line(data = Gland_UICN, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_UICN, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_UICN, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_UICN")

ggplot()+
  geom_line(data = Gland_Montoly, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Montoly, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Montoly, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Montoly")

ggplot()+
  geom_line(data = Gland_Grand_Rue, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Grand_Rue, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Grand_Rue, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Grand_Rue")

ggplot()+
  geom_line(data = Gland_La_Falaise, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Falaise, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Falaise, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Falaise")

ggplot()+
  geom_line(data = Gland_La_Lignière, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Lignière, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Lignière, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Lignière")

ggplot()+
  geom_line(data = Gland_Eikenott, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Eikenott, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Eikenott, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Eikenott")

ggplot()+
  geom_line(data = Gland_La_Dôle, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Dôle, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Dôle, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Dôle")

ggplot()+
  geom_line(data = Gland_En_Bord, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_En_Bord, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_En_Bord, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_En_Bord")

```

We select just the bike and the date data for the interested point, we convert everything into tsibble data, and we set date column as index. Doing so, now we have a time series for the bike data at the interested point and it will be easier to build models and to use the autoplot function. After that we will repeat the process for the ebike data, and after this we will do it for the next point.

## Gland Les Tuillières
```{r}
#Bike data 
Gland_Les_Tuillières_Bike_tsibble <- as_tsibble(Gland_Les_Tuillières%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Les_Tuillières_E_Bike_tsibble <- as_tsibble(Gland_Les_Tuillières%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Les_Tuillières_Bike_tsibble)
autoplot(Gland_Les_Tuillières_E_Bike_tsibble)
```

## Gland Swissquote
```{r}
#Bike data 
Gland_Swissquote_Bike_tsibble <- as_tsibble(Gland_Swissquote%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Swissquote_E_Bike_tsibble <- as_tsibble(Gland_Swissquote%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Swissquote_Bike_tsibble)
autoplot(Gland_Swissquote_E_Bike_tsibble)
```

## Gland Gare Sud
```{r}
#Bike data 
Gland_Gare_Sud_Bike_tsibble <- as_tsibble(Gland_Gare_Sud%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Gare_Sud_E_Bike_tsibble <- as_tsibble(Gland_Gare_Sud%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Gare_Sud_Bike_tsibble)
autoplot(Gland_Gare_Sud_E_Bike_tsibble)
```

## Gland UICN
```{r}
#Bike data 
Gland_UICN_Bike_tsibble <- as_tsibble(Gland_UICN%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_UICN_E_Bike_tsibble <- as_tsibble(Gland_UICN%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_UICN_Bike_tsibble)
autoplot(Gland_UICN_E_Bike_tsibble)
```

## Gland Montoly
```{r}
#Bike data 
Gland_Montoly_Bike_tsibble <- as_tsibble(Gland_Montoly%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Montoly_E_Bike_tsibble <- as_tsibble(Gland_Montoly%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Montoly_Bike_tsibble)
autoplot(Gland_Montoly_E_Bike_tsibble)
```

## Gland Grand'Rue
```{r}
#Bike data 
Gland_Grand_Rue_Bike_tsibble <- as_tsibble(Gland_Grand_Rue%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Grand_Rue_E_Bike_tsibble <- as_tsibble(Gland_Grand_Rue%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Grand_Rue_Bike_tsibble)
autoplot(Gland_Grand_Rue_E_Bike_tsibble)
```

## Gland La Falaise
```{r}
#Bike data 
Gland_La_Falaise_Bike_tsibble <- as_tsibble(Gland_La_Falaise%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_La_Falaise_E_Bike_tsibble <- as_tsibble(Gland_La_Falaise%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_La_Falaise_Bike_tsibble)
autoplot(Gland_La_Falaise_E_Bike_tsibble)
```

## Gland La Liginière
```{r}
#Bike data 
Gland_La_Lignière_Bike_tsibble <- as_tsibble(Gland_La_Lignière%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_La_Lignière_E_Bike_tsibble <- as_tsibble(Gland_La_Lignière%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_La_Lignière_Bike_tsibble)
autoplot(Gland_La_Lignière_E_Bike_tsibble)
```

## Gland Eiekenott
```{r}
#Bike data 
Gland_Eikenott_Bike_tsibble <- as_tsibble(Gland_Eikenott%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Eikenott_E_Bike_tsibble <- as_tsibble(Gland_Eikenott%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Eikenott_Bike_tsibble)
autoplot(Gland_Eikenott_E_Bike_tsibble)
```

## Gland La Dôle
```{r}
#Bike data 
Gland_La_Dôle_Bike_tsibble <- as_tsibble(Gland_La_Dôle%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_La_Dôle_E_Bike_tsibble <- as_tsibble(Gland_La_Dôle%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_La_Dôle_Bike_tsibble)
autoplot(Gland_La_Dôle_E_Bike_tsibble)
```

## Gland En Bord
```{r}
#Bike data 
Gland_En_Bord_Bike_tsibble <- as_tsibble(Gland_En_Bord%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_En_Bord_E_Bike_tsibble <- as_tsibble(Gland_En_Bord%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_En_Bord_Bike_tsibble)
autoplot(Gland_En_Bord_E_Bike_tsibble)
```

We convert the two Gland_fin and Gland_fin_2 dataset into tsibble data.
```{r}
Gland_fin_tsibble <- as_tsibble(Gland_fin, index = Date)
```

```{r}
Gland_fin_2_tsibble <- as_tsibble(Gland_fin_2, index = Date)
```




In all the station the capacity is far away from beiing reach. 

