---
title: "Eda"
output: html_document
date: '2022-05-15'
---

#Load every library needed
```{r, echo = FALSE, message = FALSE}
source(here::here("Setup/setup.R"))
```

### Part 2 : Exploratory Data Analysis (EDA)


We first look at the data. we are interested in forecasting the numbers of bike and ebike needed in the different stations, so here we plot the number of this 2 variables and the stations capacities sorted by time.
```{r}

ggplot()+
  geom_line(data = Gland_Les_Tuillières, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Les_Tuillières, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Les_Tuillières, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Les_Tuillières")

ggplot()+
  geom_line(data = Gland_Swissquote, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Swissquote, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Swissquote, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Swissquote")

ggplot()+
  geom_line(data = Gland_Gare_Sud, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Gare_Sud, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Gare_Sud, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Gare_Sud")

ggplot()+
  geom_line(data = Gland_UICN, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_UICN, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_UICN, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_UICN")

ggplot()+
  geom_line(data = Gland_Montoly, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Montoly, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Montoly, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Montoly")

ggplot()+
  geom_line(data = Gland_Grand_Rue, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Grand_Rue, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Grand_Rue, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Grand_Rue")

ggplot()+
  geom_line(data = Gland_La_Falaise, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Falaise, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Falaise, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Falaise")

ggplot()+
  geom_line(data = Gland_La_Lignière, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Lignière, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Lignière, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Lignière")

ggplot()+
  geom_line(data = Gland_Eikenott, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Eikenott, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Eikenott, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Eikenott")

ggplot()+
  geom_line(data = Gland_La_Dôle, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Dôle, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Dôle, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Dôle")

ggplot()+
  geom_line(data = Gland_En_Bord, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_En_Bord, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_En_Bord, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_En_Bord")

```

1. Gland_Les_Tuillières : No clear trend or seasonality 
2. Gland_Swissquote : No clear trend or seasonality 
3. Gland_Gare_Sud : No clear trend or seasonality 
4. Gland_UICN : Some movement and maybe a little bit of seasonality 
5. Gland_Montoly : No clear trend or seasonality 
6. Gland_Grande_Rue : Some movement and maybe a little bit of seasonality 
7. Gland_La_Falaise : No clear trend or seasonality 
8. Gland_La_Lignère : No clear trend or seasonality 
9. Gland_Eikenott : Some movement in the trend and maybe a little bit of seasonality
10. Gland_La_Dôle : No clear trend or seasonality 
11. Gland_En_Bord : Almost zero pattern (no movement of the line)
In all the station the capacity is far away from beiing reach. 

