---
title: "Untitled"
output: html_document
date: '2022-05-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load every library needed
```{r, echo = FALSE, message = FALSE}
source(here::here("Setup/setup.R"))
```
#Load the dataset
```{r}
setwd(here::here("Data/")) # Where are the data sets
load("Bikesharing_dataset.RData")
```
#Building the dataset for every station needed and converting it as a dataframe + renameing the needed columns
```{r}
Gland_Les_Tuillières <- as.data.frame(series["Gland, Les Tuillières"])
colnames(Gland_Les_Tuillières) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Swissquote <- as.data.frame(series["Gland, Swissquote"])
colnames(Gland_Swissquote) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Gare_Sud1 <- as.data.frame(series["Gland, Gare Sud, travaux, déplacée de 20m en mars-avril"])
colnames(Gland_Gare_Sud1) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Gare_Sud2 <-  as.data.frame(series["Gland, Gare Sud, travaux, déplacée de 40m a nord en mars-avril"])
colnames(Gland_Gare_Sud2) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_UICN <- as.data.frame(series["Gland, UICN"])
colnames(Gland_UICN) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Montoly <- as.data.frame(series["Gland, Montoly"])
colnames(Gland_Montoly) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Grand_Rue <- as.data.frame(series["Gland, Grand'Rue"])
colnames(Gland_Grand_Rue) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_La_Falaise <- as.data.frame(series["Gland, La Falaise"])
colnames(Gland_La_Falaise) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_La_Lignière <- as.data.frame(series["Gland, La Lignière"])
colnames(Gland_La_Lignière) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_Eikenott <- as.data.frame(series["Gland, Eikenott"])
colnames(Gland_Eikenott) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_La_Dôle <- as.data.frame(series["Gland, La Dôle"])
colnames(Gland_La_Dôle) <- c("Bike","E_Bike","Capacity","Date","Name")

Gland_En_Bord <- as.data.frame(series["Gland, En Bord"])
colnames(Gland_En_Bord) <- c("Bike","E_Bike","Capacity","Date","Name")

```


#searching for NA values
```{r}
which(is.na(Gland_Les_Tuillières))
which(is.na(Gland_Swissquote))
which(is.na(Gland_Gare_Sud1))
which(is.na(Gland_Gare_Sud2))
which(is.na(Gland_UICN))
which(is.na(Gland_Montoly))
which(is.na(Gland_Grand_Rue))
which(is.na(Gland_La_Falaise))
which(is.na(Gland_La_Lignière))
which(is.na(Gland_Eikenott))
which(is.na(Gland_La_Dôle))
which(is.na(Gland_En_Bord))
```
#Look at the 2 dataset with NA values (both grare sud)
#Gland Gare is composed by 2 dataset with null data because of works changement -> eliminate the null data and bind in a unique dataset 
```{r}
Gland_Gare_Sud1 <- Gland_Gare_Sud1[c(1:256), ]

Gland_Gare_Sud2 <- Gland_Gare_Sud2[c(257:1975), ]

Gland_Gare_Sud <- bind_rows(Gland_Gare_Sud1, Gland_Gare_Sud2)
Gland_Gare_Sud
```

# the first 117 rows are 1 per our and not every 10 minuts -> eliminate
```{r}
Gland_Eikenott <- Gland_Eikenott[c(118:1975), ]
Gland_En_Bord <- Gland_En_Bord[c(118:1975), ]
Gland_Gare_Sud <- Gland_Gare_Sud[c(118:1975), ]
Gland_Grand_Rue <- Gland_Grand_Rue[c(118:1975), ]
Gland_La_Dôle <- Gland_La_Dôle[c(118:1975), ]
Gland_La_Falaise <- Gland_La_Falaise[c(118:1975), ]
Gland_Les_Tuillières <- Gland_Les_Tuillières[c(118:1975), ]
Gland_Montoly <- Gland_Montoly[c(118:1975), ]
Gland_Swissquote <- Gland_Swissquote[c(118:1975), ]
Gland_UICN <- Gland_UICN[c(118:1975), ]
Gland_La_Lignière <- Gland_La_Lignière[c(118:1975), ]
```
#first look at the data. we are interested in forecasting the numbers of bike and ebike needed in the different stations, so here we plot the number of this 2 variables and the stations capacities sorted by time.
```{r}

ggplot()+
  geom_line(data = Gland_Les_Tuillières, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Les_Tuillières, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Les_Tuillières, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Les_Tuillières")

ggplot()+
  geom_line(data = Gland_Swissquote, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Swissquote, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Swissquote, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Swissquote")

ggplot()+
  geom_line(data = Gland_Gare_Sud, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Gare_Sud, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Gare_Sud, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Gare_Sud")

ggplot()+
  geom_line(data = Gland_UICN, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_UICN, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_UICN, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_UICN")

ggplot()+
  geom_line(data = Gland_Montoly, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Montoly, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Montoly, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Montoly")

ggplot()+
  geom_line(data = Gland_Grand_Rue, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Grand_Rue, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Grand_Rue, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Grand_Rue")

ggplot()+
  geom_line(data = Gland_La_Falaise, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Falaise, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Falaise, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Falaise")

ggplot()+
  geom_line(data = Gland_La_Lignière, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Lignière, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Lignière, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Lignière")

ggplot()+
  geom_line(data = Gland_Eikenott, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_Eikenott, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_Eikenott, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_Eikenott")

ggplot()+
  geom_line(data = Gland_La_Dôle, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_La_Dôle, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_La_Dôle, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_La_Dôle")

ggplot()+
  geom_line(data = Gland_En_Bord, aes(y=Bike, x=Date, color = "Bike"), size=1) +
  geom_line(data = Gland_En_Bord, aes(y=E_Bike, x=Date, Color = "E_bike"), size=1) +
  geom_line(data = Gland_En_Bord, aes(y=Capacity, x=Date, color = "Capacity"), size=1) +
  scale_color_manual(values = c("Bike"="blue","E_bike"="black","Capacity"="red")) +
  labs(color = "Legend") +
  ggtitle("Gland_En_Bord")

```



#We select just the bike and the date data for the interested point, we convert everything into tsibble data, and we set date column as index. Doing so, now we have a time series for the bike data at the interested point and it will be easier to build models and to use the autoplot function. After that we will repeat the process for the ebike data, and after this we will do it for the next point.

## Gland Les Tuillières
```{r}
#Bike data 
Gland_Les_Tuillières_Bike_tsibble <- as_tsibble(Gland_Les_Tuillières%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Les_Tuillières_E_Bike_tsibble <- as_tsibble(Gland_Les_Tuillières%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Les_Tuillières_Bike_tsibble)
autoplot(Gland_Les_Tuillières_E_Bike_tsibble)
```

## Gland Swissquote
```{r}
#Bike data 
Gland_Swissquote_Bike_tsibble <- as_tsibble(Gland_Swissquote%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Swissquote_E_Bike_tsibble <- as_tsibble(Gland_Swissquote%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Swissquote_Bike_tsibble)
autoplot(Gland_Swissquote_E_Bike_tsibble)
```

## Gland Gare Sud
```{r}
#Bike data 
Gland_Gare_Sud_Bike_tsibble <- as_tsibble(Gland_Gare_Sud%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Gare_Sud_E_Bike_tsibble <- as_tsibble(Gland_Gare_Sud%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Gare_Sud_Bike_tsibble)
autoplot(Gland_Gare_Sud_E_Bike_tsibble)
```

## Gland UICN
```{r}
#Bike data 
Gland_UICN_Bike_tsibble <- as_tsibble(Gland_UICN%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_UICN_E_Bike_tsibble <- as_tsibble(Gland_UICN%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_UICN_Bike_tsibble)
autoplot(Gland_UICN_E_Bike_tsibble)
```

## Gland Montoly
```{r}
#Bike data 
Gland_Montoly_Bike_tsibble <- as_tsibble(Gland_Montoly%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Montoly_E_Bike_tsibble <- as_tsibble(Gland_Montoly%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Montoly_Bike_tsibble)
autoplot(Gland_Montoly_E_Bike_tsibble)
```

## Gland Grand'Rue
```{r}
#Bike data 
Gland_Grand_Rue_Bike_tsibble <- as_tsibble(Gland_Grand_Rue%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Grand_Rue_E_Bike_tsibble <- as_tsibble(Gland_Grand_Rue%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Grand_Rue_Bike_tsibble)
autoplot(Gland_Grand_Rue_E_Bike_tsibble)
```

## Gland La Falaise
```{r}
#Bike data 
Gland_La_Falaise_Bike_tsibble <- as_tsibble(Gland_La_Falaise%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_La_Falaise_E_Bike_tsibble <- as_tsibble(Gland_La_Falaise%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_La_Falaise_Bike_tsibble)
autoplot(Gland_La_Falaise_E_Bike_tsibble)
```

## Gland La Liginière
```{r}
#Bike data 
Gland_La_Lignière_Bike_tsibble <- as_tsibble(Gland_La_Lignière%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_La_Lignière_E_Bike_tsibble <- as_tsibble(Gland_La_Lignière%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_La_Lignière_Bike_tsibble)
autoplot(Gland_La_Lignière_E_Bike_tsibble)
```

## Gland Eiekenott
```{r}
#Bike data 
Gland_Eikenott_Bike_tsibble <- as_tsibble(Gland_Eikenott%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_Eikenott_E_Bike_tsibble <- as_tsibble(Gland_Eikenott%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_Eikenott_Bike_tsibble)
autoplot(Gland_Eikenott_E_Bike_tsibble)
```

## Gland La Dôle
```{r}
#Bike data 
Gland_La_Dôle_Bike_tsibble <- as_tsibble(Gland_La_Dôle%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_La_Dôle_E_Bike_tsibble <- as_tsibble(Gland_La_Dôle%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_La_Dôle_Bike_tsibble)
autoplot(Gland_La_Dôle_E_Bike_tsibble)
```

## Gland En Bord
```{r}
#Bike data 
Gland_En_Bord_Bike_tsibble <- as_tsibble(Gland_En_Bord%>%
  dplyr::select(Date, "Bike"= Bike), index = Date)

#Ebike data
Gland_En_Bord_E_Bike_tsibble <- as_tsibble(Gland_En_Bord%>%
  dplyr::select(Date, "E_Bike"= E_Bike), index = Date)

#autoplot
autoplot(Gland_En_Bord_Bike_tsibble)
autoplot(Gland_En_Bord_E_Bike_tsibble)
```



# exemple of model taken by proff class
```{r}
'fit <- Gland_Les_Tuillières_Bike_ts %>%
model(ETS(Bike ~ error("A") + trend("N", alpha = 0.1) + season("N")))
fit %>% forecast(h = 10) %>% autoplot(Gland_Les_Tuillières_Bike_ts, level = 0) +
theme(legend.position = "none")'
```
### Another possibility 

```{r}
Gland_tot <- bind_cols(Gland_Eikenott, Gland_En_Bord, Gland_Gare_Sud, Gland_Grand_Rue, Gland_La_Dôle, Gland_La_Falaise, Gland_La_Lignière, Gland_Les_Tuillières, Gland_Montoly, Gland_Swissquote, Gland_UICN)
Gland_tot_clean <- Gland_tot[-c(9,14,19,24,29,34,39,44,49,54)]

names(Gland_tot_clean)
head(Gland_tot_clean)
```


#dropping columns with station names and renaming columns
```{r}
Gland_fin <- Gland_tot_clean[-c(5,9,13,17,21,25,29,33,37,41,45)]
colnames(Gland_fin) <- c("Bike_Eikenott", "Ebike_Eikenott", "Capacity_Eikenott", "Date", "Bike_En_Bord", "Ebike_En_Bord", "Capacity_En_Bord", "Bike_Gare_Sud", "Ebike_Gare_Sud", "Capacity_Gare_Sud", "Bike_Grand_Rue", "Ebike_Grand_Rue", "Capacity_Grand_Rue", "Bike_La_Dôle", "Ebike_La_Dôle", "Capacity_La_Dôle", "Bike_La_Falaise", "Ebike_La_Falaise", "Capacity_La_Falaise", "Bike_La_Lignière", "Ebike_La_Lignière", "Capacity_La_Lignière", "Bike_Les_Tuillières", "Ebike_Les_Tuillières", "Capacity_Les_Tuillières", "Bike_Montoly", "Ebike_Montoly", "Capacity_Montoly", "Bike_Swissquote", "Ebike_Swissquote", "Capacity_Swissquote", "Bike_UICN", "Ebike_UICN", "Capacity_UICN")
head(Gland_fin)
```

#convert into tsibble data
```{r}
Gland_fin_tsibble <- as_tsibble(Gland_fin, index = Date)
Gland_fin_tsibble
```

```{r}
Gland_fin_tsibble %>% autoplot(Bike_Eikenott) +
  ylab("Bike") +
  xlab("Time") +
  ggtitle("Eikenott")
```


## NOW WE CAN DO IT FOR EVERY VARIABLE BUT FOR THE MOMENT WE WILL FOCUS ON JUST THIS ONE
## Smoothed average model first idea

```{r}
Eikenott_bike_ts_plus <- Gland_Eikenott_Bike_tsibble %>%
  mutate("MA" = slider::slide_dbl(Bike, mean, .before = 3, .after = 3, .complete = TRUE))

Eikenott_bike_ts_plus$Bike <- as.double(Eikenott_bike_ts_plus$Bike)

Eikenott_bike_ts_plus

Eikenott_bike_ts_plus %>%
  autoplot(Bike) +
  ylab("Bike") + xlab("Time") +ggtitle("Eikenott") + autolayer(Eikenott_bike_ts_plus, MA, color = "red")

```